% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode,linktoc=all}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  10pt,
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=25mm,right=25mm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\pagestyle{headings}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{british}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Policies for the use of the Induction Zone digital infrastructure},
  pdfauthor={Andy Clifton},
  pdflang={en-GB},
  pdfsubject={policiesInduction Zone},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Policies for the use of the Induction Zone digital
infrastructure}
\author{Andy Clifton}
\date{}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{1}
\tableofcontents
}
\hypertarget{about-this-document}{%
\section{About this document}\label{about-this-document}}

This document contains the policies for using the Induction Zone's
digital infrastructure. It is provided as a GitHub repository to allow
tracking.

\hypertarget{applicability}{%
\subsection{Applicability}\label{applicability}}

These policies applies to people using our digital infrastructure,
including:

\begin{itemize}
\tightlist
\item
  slack channel (\url{inductionzone.slack.com})
\item
  online file storage
\item
  messaging or contact by email, through LinkedIn, or other messaging
  services.
\item
  email marketing tools
\end{itemize}

\hypertarget{check-for-updates}{%
\subsection{Check for updates}\label{check-for-updates}}

Please check that you are using the most recent version of this
document. This can be obtained at
https://github.com/enviconnect/public-inductionzone-policies/blob/main/policies.pdf.

Archived versions can be found at
https://github.com/enviconnect/public-inductionzone-policies/releases.

\hypertarget{about-the-induction-zone}{%
\section{About the Induction Zone}\label{about-the-induction-zone}}

\hypertarget{scope-of-the-induction-zone}{%
\subsection{Scope of the Induction
Zone}\label{scope-of-the-induction-zone}}

The Induction Zone supports individuals, startups, and established
companies to find, develop, and deploy technologies to support the
generation of electricity from renewable energy sources, particularly
wind energy.

\hypertarget{operators}{%
\subsection{Operators}\label{operators}}

The Induction Zone is operated by:

TGU enviConnect TTI GmbH Nobelstrasse 15 70569 Stuttgart Germany

(henceforth refered to as ``we'', ``us'', ``our'', ``the operators'', or
``Induction Zone'').

Contact us at
\href{mailto:induction.zone@enviconnect.de}{\nolinkurl{induction.zone@enviconnect.de}}.

\hypertarget{code-of-conduct}{%
\section{Code of Conduct}\label{code-of-conduct}}

The Induction Zone is a place for people to exchange news, views, ideas,
and experience and appear authentically (i.e., speak in a way that is
aligned with their own beliefs and experience and not need to present a
facade). We encourage all users of our infrastructure to respect this
and support each other.

This does not mean that differences of opinion, or debate, are not
allowed. Instead, we encourage respectful, constructive discussion and
recognition that others' opinions are also valid.

Demeaning or derogatory language, harrasment, hate speech, or
discrimination will not be tolerated.

\hypertarget{diversity-equality-and-inclusion-dei}{%
\subsection{Diversity, equality, and inclusion
(DEI)}\label{diversity-equality-and-inclusion-dei}}

To the extent allowed by law, we strive to include anyone and everyone
in the Induction Zone regardless of gender, sexual preference, age,
national origin, educational background, or other differentiating
characteristic.

All users of the Induction Zone infrastructure are requested to follow
the same principles of respecting, supporting, and encouraging
diversity, equality, and inclusion when using the Induction Zone
infrastructure.

Please note that only persons aged 18 or over will be given access to
the Induction Zone.

\hypertarget{reporting-activities-that-go-against-the-code-of-conduct}{%
\subsection{Reporting activities that go against the code of
conduct}\label{reporting-activities-that-go-against-the-code-of-conduct}}

We encourage anyone who feels that they have experienced behaviour that
goes against this code of conduct during an Induction Zone event, or
during their use of Induction Zone infrastructure, or during any other
activity related to the Induction Zone, to contact
induction.zone@enviconnect.de with a detailed description of what
happened.

\hypertarget{how-we-will-deal-with-activities-that-go-against-the-code-of-conduct}{%
\subsection{How we will deal with activities that go against the code of
conduct}\label{how-we-will-deal-with-activities-that-go-against-the-code-of-conduct}}

If we observe activities that go against this code of conduct, or have
such reported to us, we will take steps to stop them. These steps may
include, but is not limited to:

\begin{itemize}
\tightlist
\item
  verbal or written warnings
\item
  temporary or permanent removal of access to the infrastructure
\item
  referal to applicable law enforcement.
\end{itemize}

\hypertarget{if-you-feel-that-we-have-gone-against-this-code-of-conduct}{%
\subsection{\texorpdfstring{If you feel that \emph{we} have gone against
this code of
conduct}{If you feel that we have gone against this code of conduct}}\label{if-you-feel-that-we-have-gone-against-this-code-of-conduct}}

Please contact us immediately explaining what has occurred, and we will
take steps to prevent this from happening again. This does not affect
your rights to a legal process.

\hypertarget{your-intellectual-property}{%
\section{Your intellectual property}\label{your-intellectual-property}}

Unless otherwise agreed, you retain full ownership of your intellectual
property during participation in the Induction Zone. You take full
responsibility for your intellectual property and agree to protect it at
all times. Although we take steps to manage participation in the
Induction Zone events it should be considered a public space, and you
are encouraged to treat it accordingly.

\hypertarget{how-we-use-your-data}{%
\section{How we use your data}\label{how-we-use-your-data}}

\hypertarget{slack}{%
\subsection{Slack}\label{slack}}

By joining the Induction Zone slack channel you agree:

\begin{itemize}
\tightlist
\item
  to have high-level analytics about your use of the slack channel made
  available to the administrators of the slack channel, who are
  appointed by the operators. These adminstrators do not have access to
  private messages. For more details see
  \href{https://slack.com/help/articles/360047512554-Use-channel-management-tools}{this
  article on slack.com}.
\item
  to have your profile be visible to other users of the slack channel
\item
  to receive email (including marketing) from the operators to the email
  address you used to sign up for the slack channel. These emails may be
  sent through third-party tools. You have the right to unsubscribe from
  such services directly or by emailing
  \href{mailto:induction.zone@enviconnect.de}{\nolinkurl{induction.zone@enviconnect.de}}.
\item
  to be added to our mailing list.
\end{itemize}

\hypertarget{messaging}{%
\subsection{Messaging}\label{messaging}}

By messaging us through email or other messaging services you agree:

\begin{itemize}
\tightlist
\item
  to receive email (including marketing) from the operators to the email
  address you used to contact us.
\item
  In the event that you use a direct messaging service (e.g., LinkedIn),
  we may use email addresses that are publically available in your
  profile. These emails may be sent through third-party tools.
\end{itemize}

You have the right to unsubscribe from such services directly or by
emailing
\href{mailto:induction.zone@enviconnect.de}{\nolinkurl{induction.zone@enviconnect.de}}.

\hypertarget{email-marketing}{%
\subsection{Email Marketing}\label{email-marketing}}

We may offer you opportunities to subscribe to a newsletter or register
for a mailing list.

By registering or subscribing you agree to receive emails from us that
we think are relevant to you.

These services will be provided by a third party and by subscribing or
registering you will be agreeing to their terms and conditions. These
services allow you to unsubscribe at will.

\hypertarget{data-pipelines}{%
\subsection{Data pipelines}\label{data-pipelines}}

We use \href{https://www.zapier.com}{Zapier} to synchronize data across
our services, in line with this policy. Check out their data policy,
\href{https://zapier.com/help/account/data-management/data-privacy-at-zapier}{here}.
They act as a data processor on our behalf and we remain the data
controllers.

\hypertarget{data-sharing}{%
\section{Data sharing}\label{data-sharing}}

We will not share your data with any third party.

\hypertarget{update-policy}{%
\section{Update policy}\label{update-policy}}

This policy is subject to revision without notice. The definitive
version of this policy is the most recent release at
https://github.com/enviconnect/public-inductionzone-policies/releases.

\hypertarget{feedback}{%
\section{Feedback}\label{feedback}}

We value your feedback. Please contact
\href{mailto:induction.zone@enviconnect.de}{\nolinkurl{induction.zone@enviconnect.de}}
with any feedback you want to share.

\end{document}
